Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_4-db_struct.tex
Misc fixes on references

\subsubsection{Parameter} - Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
While defining a parameter, there are three required fields which need to be provided such as variable, unit and parametertype.
\begin{itemize}  
  \item \emph{Variable} - Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
  \item \emph{Unit} - metric unit of measuring
  \item \emph{Parameter Type} - Should be one of 'Instantaneous', 'Accumulative', 'Mean'
  \begin{lstlisting}[language=Python]
    {
      "parameterId": "O.Precipitation",
      "variable": "Precipitation",
      "unit": "mm",
      "parameterType": "Instantaneous"
    }
  \end{lstlisting}
\end{itemize}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/hierarchical_database.jpg}
    \caption{Hierarchical database}
    \label{fi:hierarchical_database}
\end{figure}

WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \ref{micro_database_per_service}.
Following chapters described the usage of databases in WDIAS and reason behind the selection.

@@

Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \ref{micro_database_per_service}.
But further, it split into two services, refering to the \ref{micro_z_axis_scaling} data is partitioned among few servers based on valueType key attribute of timeseries.
Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.

@@

\acrshort{wdias} is using \acrshort{mongodb} as the Document-oriented databse, since it has the Geo searching capabilities.
\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports;
\begin{itemize}
  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}. Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
\ref{micro_y_axis_scaling} concept is using here by splitting into the multiple services based on the functionality and scale the system.

>>>>

\subsubsection{Parameter}
Parameter describe the variable measuring against a location. All parameters ahve a unique String identifier called as parameterId. A parameter can be use in multiple locations.
While defining a parameter, there are three required fields which need to be provided such as variable, unit and parametertype.
\begin{itemize}  
  \item \emph{Variable} - Nature of the variable measuring. Example Precipitation, Temperature and WaterLevel etc
  \item \emph{Unit} - metric unit of measuring
  \item \emph{Parameter Type} - Should be one of 'Instantaneous', 'Accumulative', 'Mean'
  \begin{lstlisting}[language=Python]
    {
      "parameterId": "O.Precipitation",
      "variable": "Precipitation",
      "unit": "mm",
      "parameterType": "Instantaneous"
    }
  \end{lstlisting}
\end{itemize}

@@

\begin{figure}[htp]
    \centering
    \includegraphics[width=0.6\textwidth]{method/microservice/hierarchical_database.jpg}
    \caption{Hierarchical database}
    \label{fi:hierarchical_database}
\end{figure}

WDIAS is using a hierarchical database, with following the concept of Database per Service which is described in the \emph{Database per Service} in Section \ref{subse:database_per_service}.
Following chapters described the usage of databases in WDIAS and reason behind the selection.

@@

Two instance of \acrshort{influxdb} is using in the WDIAS system by adapter-scalar and adapter-vector services. For the scalability, the system uses \emph{Database per Service} as mentioned in Section \ref{subse:database_per_service}.
But further, it split into two services, referring to the Section \ref{subse:scale_cube}, the Z-axis scaling, the data is partitioned among few servers based on valueType key attribute of timeseries.
Which also conclude the concept of splitting into more services based on other key attributes such as timeseriesType, if further performance required.

@@

\acrshort{wdias} is using \acrshort{mongodb} as the Document-oriented databse, since it has the Geo searching capabilities.
\acrshort{mongodb} \cite{mongodbMongoDBManual} is a general purpose, document-based, distributed database. And it supports;
\begin{itemize}
  \item Supports query operations on geo-spatial data \cite{mongodbMongoDBManual}
  \item Clustering and Sharding available for scalability and reliability
\end{itemize}
\acrshort{mongodb} geo-spatial features are using for support Geo queries in the WDIAS. Other than that, external timeseries metadata queries are served by the indexed timeseries metadata data.
If metadata not present in the adapter-query, if fetch data from the adapter-metadata, then indexed and cache in the \acrshort{mongodb}. Vise a versa, if new timeseries create in the adapter-metadata, it trigger an event to adapter-query to index the new timeseries.
In Section \ref{subse:scale_cube}, the Y-axis scaling concept is using here by splitting into the multiple services based on the functionality and scale the system.
